---
title: Nikhil Kaza
graphics: no
name: Nikhil
surname: Kaza
headcolor: 414141
#qualifications: 
address: "110 New East, Chapel Hill, NC 27599-3140"
phone: "+1 919 962 4767"
www: nkaza.github.io
email: "nkaza@unc.edu"
github: nkaza
date: '`r format(Sys.Date(), "%B %d, %Y")`'
#csl: "csl/chicago-author-date.csl"
csl: "csl/apa7-cv-nk-edition.csl"
header-includes:
  # allow URLs to break at any character
  - \usepackage{xurl}
  - \usepackage{longtable}
  - \geometry{left=2.5cm, top=2cm, right=2.5cm, bottom=1cm, footskip=.4cm}

  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \fancyhf{}
  # - \fancyhead[R]{\thepage}

knit: (function(input, ...) {lapply(bookdown::render_book(input, output_file = "docs/nkaza_CV", output_format = "all", envir = globalenv(), ...), browseURL)})

---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(vroom)
source("R/pretty.R")

```

<!--chapter:end:index.Rmd-->

# Education

```{r education}
vroom::vroom("data/education.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:education.Rmd-->

# Experience

```{r appointment}
vroom::vroom("data/appointment.csv") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what, when, with, where, why)
```

<!--chapter:end:appointment.Rmd-->


# Grants

```{r grantstable, results='asis'}

grants <- read_csv('data/grant.csv')

sumgrants <- grants |>
  pull(total_costs) |>
  sum(na.rm = TRUE)


onlydirectcosts <- FALSE

grants <-
    if(onlydirectcosts)
    rename(grants, Amount = direct_costs) else
        rename(grants, Amount = total_costs)

sumgrants <- grants |>
  pull(Amount) |>
  sum(na.rm = TRUE)


grants |>
  mutate(
    Time = paste0(start, ifelse(is.na(end), "", paste0("--", end))),
    Entry = paste( "``", title, "''\t",
      "\\emph{", funding_agency, "}",
      sep = ""
    ),
    Amount = dollars(Amount)
  ) |>
  arrange(desc(Time), desc(Amount)) |>
  select(Time, Entry, Amount) %>%
  baretable(align = "llp{11.3cm}r",
            longtable =TRUE)

# Bare table is from Rob Hyndman's CV template. See pretty.R. Eventually need to create one that will work for html/doc
```

I have acquired (in most cases jointly) $`r sprintf("%2.1f", sumgrants/1e6)` million in  research grants. 

<!--chapter:end:grant.Rmd-->

# Publications

```{r}
pubs <- vitae::bibliography_entries("bib/kaza.bib") 


# Google scholar stats
get_gcites <- function(date) {
  "https://scholar.google.com/citations?hl=en&user=F0FfN00AAAAJ" |>
    gcite::gcite_url() |>
    gcite::gcite_citation_index()
}

# Get Google scholar citation data
get_scholar_cites <- function(date) {
  # Need to load in lots of 100 to avoid connection issues
  gspapers <- list()
  complete <- FALSE
  while (!complete) {
    k <- length(gspapers)
    gspapers[[k + 1]] <- gcite::gcite_url(
        url = "https://scholar.google.com/citations?hl=en&user=F0FfN00AAAAJ",
        cstart = k * 100,
        pagesize = 100
      ) |>
      gcite::gcite_papers() |>
      suppressWarnings()
    if (NROW(gspapers[[k + 1]]) < 100) {
      complete <- TRUE
    }
  }
  dplyr::bind_rows(gspapers) |>
    tibble::as_tibble()
}


```



## Refereed Journal Papers

```{r}
articles <- pubs%>%
    filter(type == "article-journal") %>%
    filter(!(id %in% c('Kaza:2015review', "Kaza:2012review", "Kaza:2009review"))) # Book Reviews
```

According to Google Scholar, the  **`r nrow(articles)`** articles (co-)authored by me have been cited **`r get_gcites()[1,"All"] %>% prettyNum(big.mark=",")`** times.

```{r}
articles %>%
    arrange(desc(issued$year))
```

## Book Reviews

```{r}
reviews <- pubs%>%
    filter(type == "article-journal") %>%
    filter(id %in% c('Kaza:2015review', "Kaza:2012review", "Kaza:2009review")) # Book Reviews

reviews %>%
    arrange(desc(issued$year))
```

## Manuscripts


```{r}
manusc <- pubs%>%
    filter(type == "manuscript")
```

Manuscripts in progress/submitted/accepted:  **`r nrow(manusc)`**

```{r}
manusc
```

## Book Chapters

```{r}
chaps <- pubs%>%
    filter(type == "chapter")
```

Total number of chapters in collected volumes:   **`r nrow(chaps)`**

```{r}
chaps %>% arrange(desc(issued$year))
```


<!--chapter:end:publication.Rmd-->

# Presentations

```{r}
pubs <- vitae::bibliography_entries("bib/kaza.bib") 

```

## Invited Talks

```{r, results='asis'}
vroom::vroom('data/talk.csv') |>
    arrange(desc(when)) |>

    mutate(entry = paste0( "\\emph{", title, "}" )) |>
    select(when, location, entry) |>
    baretable(align = "llp{6cm}l")
    
```



## Conference Presentations (Selected)

```{r}
presentations <- pubs%>%
    filter(type == "paper-conference") %>%
    arrange(desc(issued$year))

presentations

```



<!--chapter:end:presentations.Rmd-->

# Teaching Activities

## Instructor

```{r courses, results='asis'}
vroom::vroom("data/teaching.csv") %>%
    group_by(Title) %>%
    mutate(count = n()) %>%
    arrange(desc(count), Year) %>%
    mutate(term_year = paste(Term, Year, sep = " "),
            term_enroll = paste0(term_year, "(", Enrollment, ")") 
           ) %>%
    summarize(Course_number = first(Course_number), 
              count = first(count),
              term_enroll = paste(term_enroll, collapse = " ")) %>%
    arrange(desc(count)) %>%
    select(Course_number, Title, term_enroll) %>%
    baretable(align = "llp{4.5cm}p{9.5cm}")
    
    
```


## Dissertation Committee Chair

```{r phdchair, results='asis'}
vroom::vroom("data/diss_committee.csv") %>%
    filter(role == "Chair") %>%
    arrange(desc(grad_year)) %>%
    select(grad_year, student, title) %>%
    baretable(align = "llp{3cm}p{12cm}",)
```


## Dissertation Commmittee Member

```{r phdcommittees, results='asis'}
vroom::vroom("data/diss_committee.csv") %>%
    filter(role == "Member") %>%
    arrange(desc(grad_year)) %>%
    select(grad_year, student, title) %>%
    baretable(    align = "llp{3cm}p{12cm}")
```

## Comprehensive Exam Commmittee Member

```{r compcommittees, results = "asis"}
vroom::vroom("data/comp_committee.csv") %>%
    arrange(grad_year) %>%
    mutate(final = if_else(is.na(grad_year), student, paste0(student, "(", grad_year, ")"))) %>%
    pull(final) %>%
    paste(collapse = ", ") %>%
    cat()

```

<!--chapter:end:teaching.Rmd-->

# Service


## Other Professional Activities
```{r otheractivities, results='asis'}

activities <- read_csv('data/service.csv') |>
           mutate(end = if_else(end == "till-date", year(today()) |> as.character(), end))

activities |>
    filter(University != "U") |>
    arrange(desc(end)) |>
  mutate(
    Time = paste0(start, ifelse(is.na(end), "", paste0("--", end))),
    Entry = what,
  ) |>
  arrange(desc(Time)) |>
  select(Time, Entry) |>
  baretable(align = "llp{11.3cm}")


```

Reviewer for

```{r reviews, results='asis'}
reviewer <- read_csv('data/review_requests.csv') |>
    pull(journal_title) |>
    unique()

paste0("\\emph{", reviewer, "}", collapse = ", ") %>% cat()
```

## University Service

```{r uniservice, results='asis'}
activities |>
    filter(University == "U") |>
    arrange(desc(end)) |>
  mutate(
    Time = paste0(start, ifelse(is.na(end), "", paste0("--", end))),
    Entry = what,
  ) |>
  arrange(desc(Time)) |>
  select(Time, Entry) |>
  baretable(align = "llp{11.3cm}")

```

<!--chapter:end:service.Rmd-->

