%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Nikhil}{Kaza}

\address{314 New East, Chapel Hill, NC 27599-3140}

\mobile{+1 919 962 4767}
\email{\href{mailto:nkaza@unc.edu}{\nolinkurl{nkaza@unc.edu}}}
\homepage{nkaza.github.io}
\github{nkaza}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{xurl}

% Pandoc CSL macros
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June 02, 2024}
    {Nikhil Kaza~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\section{Education}\label{education}

\begin{cventries}
    \cventry{Ph.D. in Regional Planning}{University of Illinois}{Urbana Champaign}{2008}{\begin{cvitems}
\item Dissertation Title: ``Reasoning with Plans: Inference of Semantic Relationships among Plans about Urban Development''
\end{cvitems}}
    \cventry{M.S. in Applied Mathematics}{University of Illinois}{Urbana Champaign}{2007}{}\vspace{-4.0mm}
    \cventry{M.U. P. in Urban Planning}{University of Illinois}{Urbana Champaign}{2004}{}\vspace{-4.0mm}
    \cventry{B.Arch (Hons.) in Architecture}{Indian Institute of Technology}{Kharagpur, India}{2001}{}\vspace{-4.0mm}
\end{cventries}

\section{Experience}\label{experience}

\begin{cventries}
    \cventry{Professor}{Department of City \& Regional Planning}{University of North Carolina at Chapel Hill}{Jul 2021 - Present}{}\vspace{-4.0mm}
    \cventry{Director}{Center for Urban \& Regional Studies}{University of North Carolina at Chapel Hill}{Jul 2021 -Jul 2024}{}\vspace{-4.0mm}
    \cventry{Adjunct Associate Professor}{Environment, Ecology \& Energy Program}{University of North Carolina at Chapel Hill}{Jul 2016 - Jul 2024}{}\vspace{-4.0mm}
    \cventry{Host Professor}{School of Architecture, Civil \& Environmental Engineering}{Ecole Polytechnique Fédérale de Lausane}{Jan 2019 - May 2019}{}\vspace{-4.0mm}
    \cventry{Associate Professor}{Department of City \& Regional Planning}{University of North Carolina at Chapel Hill}{Jul 2015  - Jul 2021}{}\vspace{-4.0mm}
    \cventry{Associate Chair}{Department of City \& Regional Planning}{University of North Carolina at Chapel Hill}{Jul 2015  - Jul 2017}{}\vspace{-4.0mm}
    \cventry{Assistant Professor}{Department of City \& Regional Planning}{University of North Carolina at Chapel Hill}{Jul 2009  - Jul 2015}{}\vspace{-4.0mm}
    \cventry{Adjunct Assistant Professor}{Curriculum of Ecology \& Environment}{University of North Carolina at Chapel Hill}{Jan 2012 - Jul 2016}{}\vspace{-4.0mm}
    \cventry{Sustainability Systems Modeler}{EDAW Inc.}{Washington, DC}{Jan 2008 - Dec 2008}{}\vspace{-4.0mm}
    \cventry{Post Doctoral Fellow}{National Center for Smart Growth Research \& Education}{University of Maryland at College Park}{Nov 2007 - Jun 2009}{}\vspace{-4.0mm}
\end{cventries}

\section{Grants}\label{grants}

\subsection{Awarded Grants}\label{awarded-grants}

\begin{itemize}
\item
  ``Beyond Visuals: Improving Accessibility of Data Curation and
  Multi-Modal Representations for People of all Abilities through
  Reproducible Workflows,'' PI, Institute of Museum and Library Services
  (IMLS) Laura Bush 21st Century Librarian Program, Grant
  \#RE-254891-OLS-23, \$649,921, Aug 2023 - July 2026 (ongoing).
\item
  ``Promoting Computational Thinking Skills for Blind and Visually
  Impaired Teens through Accessible Library Makerspaces,'' PI, Institute
  of Museum and Library Services (IMLS) National Leadership Grants,
  Grant \#LG-252360-OLS-22, \$498,638, Aug 2022 - May 2025 (ongoing).
\item
  ``Inclusive Data Science: Fostering Accessibility and Reproducibility
  with Multimodal Learning Strategies,'' PI, Teach Access Faculty
  Grants, Tier 3, \$5,000, May 2023 - May 2024 (ongoing).
\item
  ``Improving Accessible Reproducibility for Data Science Publishing
  System,'' PI, Posit PBC (unrestricted gift), \$54,327, May 2022 -
  Present (ongoing).
\item
  ``Co-designing an Alexa-Based Conversational mHealth System with
  Visually Impaired People to Promote Physical Activities,'' Co-PI,
  Center on Health, Aging, and Disability's (CHAD) Pilot Grant Program
  at the University of Illinois at Urbana-Champaign, \$29,866, 2023-2024
  (ongoing).
\item
  ``Category I: Crossing the Divide Between Today's Practice and
  Tomorrow's Science,'' Senior Personnel, National Science Foundation
  (NSF), Grant \#2005572, \$10,000,000.00, Oct 2021 - Sept 30, 2026 (.5
  FTE academic year) (ongoing).
\item
  ``Insight without Sight: Enhancing Data Literacy through Multimodal
  Data Science Education - Smith-Kettlewell Summer Institute,'' Subaward
  PI, Rehabilitation Engineering Research Centers (RERC) Program: RERC
  on Blindness and Low Vision, National Institute on Disability,
  Independent Living, and Rehabilitation Research (NIDILRR), Grant
  \#90REGE0018-01-00, \$11,975, July 17, 2023 - August 11, 2023
  (completed).
\item
  ``Data Accessibilization: Making Data Science Education Accessible for
  Blind Learners,'' PI, Wallace Foundation, Emerging Scholars Program,
  International Society of the Learning Sciences, \$10,000, Jan 2022 -
  Dec 2022 (completed).
\end{itemize}

\subsection{Under-Review Grants}\label{under-review-grants}

\begin{itemize}
\tightlist
\item
  ``Collaborative Research: SpatioTemporal Representations for
  Information and Data Equity: An Interactive AudioTactile System for
  BVI Data Scientists,'' PI (at UIUC), National Science Foundation
  (NSF), Workplace Equity for Persons with Disabilities in STEM and STEM
  Education (nsf23593), \$573,548 (for UIUC) out of \$1,499,917 total,
  July 2024 - June 2028 (under review).
\end{itemize}

\section{Publications}\label{publications}

\subsection{Refereed Journal Papers}\label{refereed-journal-papers}

\phantomsection\label{refs-d7160fc4b1472e33e971f07cf2a6101a}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-doi:10.1080ux2f09286586.2020.1863993}
Choi, Soyoung, and JooYoung Seo. 2021. {``Trends in Healthcare Research
on Visual Impairment and Blindness: Use of Bibliometrics and
Hierarchical Cluster Analysis.''} \emph{Ophthalmic Epidemiology} 28 (4):
277--84. \url{https://doi.org/10.1080/09286586.2020.1863993}.

\bibitem[\citeproctext]{ref-choiConversationalAgentsMHealth2024}
Choi, Soyoung, JooYoung Seo, Manuel Hernandez, and Spyros Kitsiou. 2024.
{``Conversational Agents in mHealth: Use Patterns, Challenges, and
Design Opportunities for Individuals with Visual Impairments.''}
\emph{Journal of Technology in Behavioral Science}, March.
\url{https://doi.org/10.1007/s41347-024-00409-7}.

\bibitem[\citeproctext]{ref-leePersonalHealthData2023}
Lee, Jarrett G. W., Kyungyeon Lee, Bongshin Lee, Soyoung Choi, JooYoung
Seo, and Eun Kyoung Choe. 2023. {``Personal Health Data Tracking by
Blind and Low-Vision People: Survey Study.''} \emph{Journal of Medical
Internet Research} 25 (1): e43917. \url{https://doi.org/10.2196/43917}.

\bibitem[\citeproctext]{ref-moonRevisitingMultimediaLearning2023}
Moon, Jewoong, Gi Woong Choi, and Joo Young Seo. 2023. {``Revisiting
Multimedia Learning Design Principles in Virtual Reality-Based Learning
Environments for Autistic Individuals.''} \emph{Virtual Reality},
September. \url{https://doi.org/10.1007/s10055-023-00856-2}.

\bibitem[\citeproctext]{ref-moonLearningAnalyticsSeamless2023a}
Moon, Jewoong, Daeyeoul Lee, Gi Woong Choi, Jooyoung Seo, Jaewoo Do, and
Taehyeong Lim. 2023. {``Learning Analytics in Seamless Learning
Environments: A Systematic Review.''} \emph{Interactive Learning
Environments} 0 (0): 1--18.
\url{https://doi.org/10.1080/10494820.2023.2170422}.

\bibitem[\citeproctext]{ref-seo2019maker}
Seo, JooYoung. 2019. {``Is the Maker Movement Inclusive of ANYONE?:
Three Accessibility Considerations to Invite Blind Makers to the Making
World.''} \emph{TechTrends} 63 (5): 514--20.
\url{https://doi.org/10.1007/s11528-019-00377-3}.

\bibitem[\citeproctext]{ref-seo2022csun}
Seo, JooYoung, and Soyoung Choi. 2022. {``Are Blind People Considered a
Part of Scientific Knowledge Producers?: Accessibility Report on Top-10
SCIE Journal Systems Using a Tripartite Evaluation Approach.''}
\emph{Journal on Technology and Persons with Disabilities}.

\bibitem[\citeproctext]{ref-seoTeachingVisualAccessibility2023}
Seo, JooYoung, and Mine Dogucu. 2023. {``Teaching Visual Accessibility
in Introductory Data Science Classes with Multi-Modal Data
Representations.''} \emph{Journal of Data Science}, March, 1--14.
\url{https://doi.org/10.6339/23-JDS1095}.

\bibitem[\citeproctext]{ref-seo2019arow}
Seo, JooYoung, and Sean McCurry. 2019. {``LaTeX Is NOT Easy: Creating
Accessible Scientific Documents with r Markdown.''} Edited by Klaus
Miesenberger, Shirley Ruiz, and Julia Santiago. \emph{Journal on
Technology and Persons with Disabilities} 7:157--71.

\bibitem[\citeproctext]{ref-seoScopingReviewThree2022}
Seo, JooYoung, Jewoong Moon, Gi Woong Choi, and Jaewoo Do. 2022. {``A
Scoping Review of Three Computational Approaches to Ethnographic
Research in Digital Learning Environments.''} \emph{TechTrends} 66 (1):
102--11. \url{https://doi.org/10.1007/s11528-021-00689-3}.

\bibitem[\citeproctext]{ref-seoSCAFFOLDingAllAbilities2021a}
Seo, JooYoung, and Gabriela T. Richard. 2021. {``SCAFFOLDing All
Abilities into Makerspaces: A Design Framework for Universal, Accessible
and Intersectionally Inclusive Making and Learning.''} \emph{Information
and Learning Sciences} 122 (11/12): 795--815.
\url{https://doi.org/10.1108/ILS-10-2020-0230}.

\end{CSLReferences}

\subsection{Papers in Refereed Conference
Proceedings}\label{papers-in-refereed-conference-proceedings}

\phantomsection\label{refs-0a0d0fd29f56a34069c75b517e1d0099}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-huh2022duoethnographic}
Huh, Mina, and JooYoung Seo. 2022. {``A Duoethnographic Study of a
Mixed-Ability Team in a Collaborative Group Programming Project.''} In
\emph{Proceedings of the 15th International Conference on
Computer-Supported Collaborative Learning - CSCL 2022}, edited by Armin
Weinberger, Wenli Chen, Davinia Hernández-Leo, and Bodong Chen, 471--74.
International Society of the Learning Sciences.

\bibitem[\citeproctext]{ref-289508}
Kaushik, Smirity, Natã M. Barbosa, Yaman Yu, Tanusree Sharma, Zachary
Kilhoffer, JooYoung Seo, Sauvik Das, and Yang Wang. 2023. {``GuardLens:
Supporting Safer Online Browsing for People with Visual Impairments.''}
In \emph{Nineteenth Symposium on Usable Privacy and Security (SOUPS
2023)}, 361--80. Anaheim, CA: USENIX Association.
\url{https://www.usenix.org/conference/soups2023/presentation/kaushik}.

\bibitem[\citeproctext]{ref-kimTrendCollaborationSTEM2023a}
Kim, Soo Hyeon, Ayoung Yoon, and JooYoung Seo. 2023. {``Trend of
Collaboration in STEM Education in Informal Learning Institutions Based
on IMLS-Funded Projects.''} \emph{Proceedings of the Association for
Information Science and Technology} 60 (1): 625--29.
\url{https://doi.org/10.1002/pra2.828}.

\bibitem[\citeproctext]{ref-konecki2017role}
Konecki, Mario, Sandra Lovrenčić, JooYoung Seo, and Charles LaPierre.
2017. {``The Role of ICT in Aiding Visually Impaired Students and
Professionals.''} \emph{Proceedings of the 11th Multidisciplinary
Academic Conference}, 148.

\bibitem[\citeproctext]{ref-lee2021collabally}
Lee, Cheuk Yin Phipson, Zhuohao Zhang, Jaylin Herskovitz, JooYoung Seo,
and Anhong Guo. 2021. {``CollabAlly: Accessible Collaboration Awareness
in Document Editing.''} In \emph{The 23rd International ACM SIGACCESS
Conference on Computers and Accessibility}, 1--4. 55.
\url{https://doi.org/10.1145/3441852.3476562}.

\bibitem[\citeproctext]{ref-leeCollabAllyAccessibleCollaboration2022a}
---------. 2022. {``CollabAlly: Accessible Collaboration Awareness in
Document Editing.''} In \emph{CHI Conference on Human Factors in
Computing Systems}, 1--17. CHI '22. New York, NY, USA: Association for
Computing Machinery. \url{https://doi.org/10.1145/3491102.3517635}.

\bibitem[\citeproctext]{ref-leeIdentifyAdaptPersist2024}
Lee, Jarrett G. W., Bongshin Lee, Soyoung Choi, JooYoung Seo, and Eun
Kyoung Choe. 2024. {``Identify, Adapt, Persist: The Journey of Blind
Individuals with Personal Health Technologies.''} \emph{Proceedings of
the ACM on Interactive, Mobile, Wearable and Ubiquitous Technologies} 8
(2): 51:1--21. \url{https://doi.org/10.1145/3659585}.

\bibitem[\citeproctext]{ref-parkExploringOnlineCommunity2023}
Park, Jaihyun, JooYoung Seo, and Jae Young Lee. 2023. {``Exploring an
Online Community of Blind Programmers by Using Topic Modeling and
Network Analysis.''} \emph{Proceedings of the Association for
Information Science and Technology} 60 (1): 1096--98.
\url{https://doi.org/10.1002/pra2.956}.

\bibitem[\citeproctext]{ref-seo2018making}
Seo, JooYoung. 2018. {``Accessibility and Inclusivity in Making:
Engaging Learners with All Abilities in Making Activities.''} In
\emph{Proceedings of the 3rd Learning Sciences Graduate Student
Conference}, 141--42. Nashville, TN: LSGSC Planning Team.

\bibitem[\citeproctext]{ref-seo2019discovering}
---------. 2019. {``Discovering Informal Learning Cultures of Blind
Individuals Pursuing STEM Disciplines: A Quantitative Ethnography Using
Listserv Archives.''} In \emph{The First International Conference on
Quantitative Ethnography: Doctoral Consortium}, S66--67. Madison, WI.

\bibitem[\citeproctext]{ref-seo2017embracing}
Seo, JooYoung, Mona AlQahtani, Xueying Ouyang, and Marcela Borge. 2017.
{``Embracing Learners with Visual Impairments in CSCL.''} In
\emph{Making a Difference: Prioritizing Equity and Access in CSCL, 12th
International Conference on Computer Supported Collaborative Learning
(CSCL) 2017}, edited by B K Smith, M Borge, E Mercier, and K Y Lim,
2:573--76. Philadelphia, PA: International Society of the Learning
Sciences (ISLS).

\bibitem[\citeproctext]{ref-teachingvisualaccessibility2022}
Seo, JooYoung, and Mine Dogucu. 2022. {``Teaching Visual Accessibility
in the Introductory Data Science Classes: Why, What, When, and How.''}
In \emph{The 2022 Symposium on Data Science \& Statistics}. Pittsburgh,
PA, USA: American Statistical Association.

\bibitem[\citeproctext]{ref-10.2312:eved.20241053}
Seo, JooYoung, Sile O'Modhrain, Yilin Xia, Sanchita Kamath, Bongshin
Lee, and James M. Coughlan. 2024. {``Designing Born-Accessible Courses
in Data Science and Visualization: Challenges and Opportunities of a
Remote Curriculum Taught by Blind Instructors to Blind Students.''} In
\emph{EuroVis 2024 - Education Papers}, edited by Robert S. and Andersen
Firat Elif E. and Laramee. The Eurographics Association.
\url{https://doi.org/10.2312/eved.20241053}.

\bibitem[\citeproctext]{ref-seo2018accessibility}
Seo, JooYoung, and Gabriela T Richard. 2018. {``Accessibility, Making
and Tactile Robotics: Facilitating Collaborative Learning and
Computational Thinking for Learners with Visual Impairments.''} In
\emph{Rethinking Learning in the Digital Age: Making the Learning
Sciences Count, 13th International Conference of the Learning Sciences
(ICLS) 2018}, edited by J Kay and R Luckin, 3:1755--57. London, UK:
International Society of the Learning Sciences (ISLS).

\bibitem[\citeproctext]{ref-seo2020coding}
---------. 2020. {``Coding Through Touch: Exploring and Re-Designing
Tactile Making Activities with Learners with Visual Dis/Abilities.''} In
\emph{Interdisciplinarity in the Learning Sciences, 14th International
Conference of the Learning Sciences (ICLS) 2020}, edited by Melissa
Gresalfi and Ilana Horn, 3:1373--80. Nashville, TN: International
Society of the Learning Sciences (ISLS).

\bibitem[\citeproctext]{ref-seoCodingNonVisuallyVisual2023}
Seo, JooYoung, and Megan Rogge. 2023. {``Coding Non-Visually in Visual
Studio Code: Collaboration Towards Accessible Development Environment
for Blind Programmers.''} In \emph{Proceedings of the 25th International
ACM SIGACCESS Conference on Computers and Accessibility}, 1--9. ASSETS
'23. New York, NY, USA: Association for Computing Machinery.
\url{https://doi.org/10.1145/3597638.3614550}.

\bibitem[\citeproctext]{ref-seoMAIDRMakingStatistical2024}
Seo, JooYoung, Yilin Xia, Bongshin Lee, Sean Mccurry, and Yu Jun Yam.
2024. {``MAIDR: Making Statistical Visualizations Accessible with
Multimodal Data Representation.''} In \emph{Proceedings of the CHI
Conference on Human Factors in Computing Systems}, 1--22. CHI '24. New
York, NY, USA: Association for Computing Machinery.
\url{https://doi.org/10.1145/3613904.3642730}.

\bibitem[\citeproctext]{ref-seoMAIDRMultimodalAccess2023}
Seo, JooYoung, Yilin Xia, Yu Jun Yam, and Sean McCurry. 2023. {``MAIDR:
Multimodal Access and Interactive Data Representation System for
Inclusive Data Science Education.''} In \emph{Proceedings of the 3rd
Annual Meeting of the International Society of the Learning Sciences},
51--54.

\bibitem[\citeproctext]{ref-289496}
Zhang, Zhuohao (Jerry), Smirity Kaushik, JooYoung Seo, Haolin Yuan,
Sauvik Das, Leah Findlater, Danna Gurari, Abigale Stangl, and Yang Wang.
2023. {``ImageAlly: A Human-AI Hybrid Approach to Support Blind People
in Detecting and Redacting Private Image Content.''} In \emph{Nineteenth
Symposium on Usable Privacy and Security (SOUPS 2023)}, 417--36.
Anaheim, CA: USENIX Association.
\url{https://www.usenix.org/conference/soups2023/presentation/zhang}.

\end{CSLReferences}

\subsection{Book Chapters}\label{book-chapters}

\phantomsection\label{refs-a989a3d82cf00293d83f5c3a7efb2b00}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-SeoDogucu2023}
Seo, JooYoung, and Mine Dogucu. 2024. {``Data Science and
Accessibility.''} In \emph{Teaching Accessible Computing}, edited by Amy
Ko, Richard Ladner, and Alannah Oleso. University of Washington.

\end{CSLReferences}

\section{Conference Presentations and Invited
Talks}\label{conference-presentations-and-invited-talks}

Seo, J. (2024, March). \emph{Unseen Insights: Empowering Autonomous Data
Science by, with, and for Blind People}. Invited talk at the UC Irvine
Donald Bren School of Information \& Computer Sciences, Irvine, CA.

Seo, J. (2023, November). \emph{Insight Over Eyesight: My Journey as a
Blind Data Scientist}. Invited talk at the Chicago Lighthouse Career
Fair, Chicago, IL (virtual).

Seo, J. (2023, November). \emph{Beyond Sight: Envisioning Data Science
Through Multimodal Access}. Invited as a keynote speaker at the 2023
UIUC iSchool's Research Showcase, Champaign, IL.

Seo, J. (2023, November). \emph{Understanding Multi-Modality of Blind
People Towards Inclusive STEM Learning}. Invited talk at the UIUC CI590
DELTA Seminar, Champaign, IL.

Seo, J. (2023, July). \emph{Screen Reader User Experience Deep Dive}.
Invited talk at the Microsoft Visual Studio Code Team, virtual.

Seo, J. (2023, June). \emph{Perceiving Beyond Vision: My Journey Through
Dreamscapes, Numerical Cognition, and a Blind Critique of Inclusive Data
Visualization}. Invited talk at the Dagstuhl Inclusive Data
Visualization Workshop, Dagstuhl, Germany.

Seo, J. (2023, May). \emph{Enhancing Accessibility in Programming and
Fostering Inclusive Data Science via Multimodal Strategies}. Invited
talk at the Campus Research Computing Consortium, virtual.

Invited panel (2023, May): \emph{Human Computer Relationships
(\textbf{Work?}): Embodiment, Inclusive Design, Accessibility, and
Emerging Technologies for Learning}, hosted by PhET Interactive
Simulations at University of Colorado Boulder.

Invited demo by Microsoft (2023, April): \emph{VSCode Accessibility}. VS
Code Day 2023: \url{https://m.youtube.com/watch?v=X3qUfOB3x8Q}

Invited panel (2022, December): \emph{Integrating Accessibility into a
Computing Career}, hosted by Associate Professor Stacy Branham at
Informatics of the University of California, Irvine. (virtual).

Seo, J. (2022, November). \emph{Accessible Library Makerspaces}. Invited
talk at the UIUC iSchool IS571: Accessibility in Library Resources,
Champaign, IL (virtual).

Seo, J. (2022, September). \emph{Digital Accessibility}. Invited panel
at the INFOcon 2022, virtual.

Seo, J. (2022, April). \emph{Accessible Data Visualization in a
Reproducible Way}. Invited talk at Champaign-Urbana Data Science User
Group, Champaign, IL (virtual).

Seo, J. (2022, March). \emph{Understanding Multi-Modality of Blind
People Towards Inclusive STEM Learning}. Invited talk at the UIUC
iSchool Proseminar, Champaign, IL (virtual).

Seo, J. (2022, March). \emph{Universal Design = Usability \texttt{*}
Accessibility (With Practical Examples Beyond Conceptual Frameworks)}.
Invited talk at INTE 535 Analysis, Implementation, and Evaluation of
Assistive Technology. Instructional Technology program of the University
of Alabama, Tuscaloosa, AL (virtual).

Seo, J. (2022, March). \emph{Your Condition is Not Your Conclusion}.
Invited talk at HTM4311: Hotel Professional Development at the Hong Kong
Polytechnic University (virtual).

Seo, J. (2021, November). \emph{SCAFFOLDing All Abilities into
Makerspaces}. Invited talk at the UIUC iSchool IS582: Make, Design, \&
Learn in Libraries, Champaign, IL (virtual).

Seo, J. (2021, October). \emph{Non-Visual Strategies for Making
Statistical-Computing Accessible}. Lightening talk at the National
Center for Supercomputing Applications, Champaign, IL.

Seo, J. (2021, September). \emph{Accessibility of Science Beyond Content
Accessibility}. Talk presented at the Argonne National Laboratory (Maths
and Computer Science Division):
\emph{\url{https://www.anl.gov/event/accessibility-of-science-beyond-content-accessibility}}.

Invited panel (2021, August). DO-IT Neuroscience for Neurodiverse
Learners Faculty panel at the University of Washington, virtual.

Seo, J. (2021, June). \emph{How to Learn to Code}. Invited Talk
presented at the Nature, Webcast:
\emph{\url{https://doi.org/10.1038/d41586-021-01638-z}}.

Seo, J., \& Richard, G. T. (2021, February). \emph{Uncovering latent
topics of blind people in computer science: structural topic modeling
for an email corpus}. Poster presented at the 2nd International
Conference on Quantitative Ethnography (ICQE), Malibu, CA.

Donegan, S. R., Porter, C., Fogel, A., Seo, J., Choi, S., \& Eagan, B.
(2021, February). \emph{U.S. media coverage during COVID-19: an
epistemic network analysis of bias, topic, and trajectory}. Poster
presented at the 2nd International Conference on Quantitative
Ethnography (ICQE), Malibu, CA.

Seo, J. (2021, January). \emph{Accessible data science beyond visual
models}. Talk presented at the rstudio::global(2021), Virtual:
\emph{\url{https://global.rstudio.com/student/page/40617}}.

Seo, J. (2020, September). \emph{Discovering knowledge sharing patterns
of blind people pursuing STEM disciplines: data science and
computational linguistics on large-scale email corpora}. Poster
presented at the Doctoral Consortium of the annual meeting of the ACM
Richard Tapia Celebration of Diversity in Computing, virtual.
\emph{Awarded the Qualcomm scholarship}.

Seo, J., \& Richard, G. T. (2020, April). \emph{Maker inclusivity =
maker accessibility: further interrogations for diverse participation}.
Poster presented at the annual meeting of the American Educational
Research Association (AERA), Virtual.

Seo, J., \& Richard, G. T. (2018, April). \emph{Furthering inclusivity
in making: a framework for accessible design of makerspaces for learners
with disabilities}. Poster presented at the annual meeting of the
American Educational Research Association (AERA), New York City, NY.

Bunag, T., Aniela, L., Nielsen, M. C., \& Seo, J. (2017, November).
\emph{The rapidly changing world of accessible online learning}.
Presented at the Panel Discussion: DDL - Accessible Online Learning In
Concurrent Presentation of the Association for Educational
Communications and Technology (AECT), Jacsonville, FL.

Seo, J. (2017, September). \emph{Tactile access to visualized
statistical data using R}. Poster presented at the annual meeting of the
ACM Richard Tapia Celebration of Diversity in Computing, Atlanta, GA.

Liao, J., Patcyk, M., Seo, J., \& Hooper, S. (2016, October).
\emph{Using hierarchical linear modeling to measure growth rate in a
gamified CBM environment}. Paper presented at the annual meeting of the
Northeastern Educational Research Association (NERA), Trumbull, CT.

Seo, J. (2016, March). \emph{Engaging blind learners in statistics study
using R}. Presented at the annual meeting of the Teaching and Learning
with Technology (TLT) Symposium, University Park, PA.

Kim, K., Seo, J., \& Clariana, R. B. (2016, March). \emph{Automatic
knowledge structure measure in online courses}. Presented at the annual
meeting of the Teaching and Learning with Technology (TLT) Symposium,
University Park, PA.

Seo, J. (2015, November). \emph{Assistive technologies for equal access
in general education}. Presented at the annual meeting of the
Association for Educational Communications and Technology (AECT),
Indianapolis, IN.

Seo, J., \& Park, E. (2015, October). \emph{The more accessible, the
more potential: simple tips for online accessibility}. Presented at the
Technology and Learning Conference, Blue Bell, PA.

\section{Media Coverage}\label{media-coverage}

\phantomsection\label{refs-232f4b001e79d047eaeb05f5ea63b847}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-heckelInformationSciencesProfessora}
Heckel, Jodi. 2023. {``Information Sciences Professor Developing Tool to
Make Data Visualizations Accessible to Blind Researchers, Students.''}
News Bureau University of Illinois Urbana-Champaign. September 29, 2023.
\url{https://news.illinois.edu/view/6367/107909242}.

\bibitem[\citeproctext]{ref-katsnelsonTheseToolsHelp2023}
Katsnelson, Alla. 2023. {``These Tools Help Visually Impaired Scientists
Read Data and Journals.''} \emph{Nature} 615 (7951, 7951): 362--63.
\url{https://doi.org/10.1038/d41586-023-00645-6}.

\bibitem[\citeproctext]{ref-mccallen2023data}
McCallen, Brian. 2023. {``Data Visualization for the Blind.''} November
3, 2023.
\url{https://speakingoutfortheblind.weebly.com/list-of-episodes-and-show-news/for-more-information-episode-329-data-visualization-tool-for-the-blind}.

\end{CSLReferences}

\section{Teaching Experience}\label{teaching-experience}

\begin{itemize}
\item
  IS 407: Introduction to Data Science (spring 2022-present).
\item
  IS 569: Internship (spring 2022). \emph{Advised Ankita Khiratkar (MS
  IM)}.
\item
  IS 589: Independent Study (spring 2022). \emph{Advised Chetna Beri (MS
  IM)}.
\item
  INFO 399: Individual Study (spring 2022). \emph{Advised Leo Zhang (CS
  undergrad --\textgreater{} Currently, Master's student at UCLA Data
  Science dept)}.
\item
  IS 389: Independent Study (spring 2022). \emph{Advised Miso Kim (BS
  IS)}.
\item
  IS 226: Introduction to Human-Computer Interaction (fall 2021).
  \emph{Co-teaching with Dr.~Yang Wang}.
\item
  Served as an annual review committee member for iSchool Ph.d. student
  Smirity Kaushik (advisor Dr.~Yang Wang) (spring 2022).
\item
  Served as a field exam committee member for iSchool Ph.D.~candidate
  Jaihyun Park (advisor Dr.~Ryan Cordell) (spring 2022).
\end{itemize}

\section{Awards and Honors}\label{awards-and-honors}

\begin{cventries}
    \cventry{Qualcomm Scholarship}{ACM Richard Tapia Celebration of Diversity in Computing Conference}{Virtual}{Sep. 2020}{\begin{cvitems}
\item Selected as one of the outstanding doctoral consortium proposals.
\end{cvitems}}
    \cventry{2020 NextGen Leaders}{Disability:IN}{Alexandria, VA}{Feb. 2020 - Jul. 2020}{\begin{cvitems}
\item Selected as one of the leaders in the U.S. for diversity.
\end{cvitems}}
    \cventry{AccessSTEM Resume contest winners Award}{AccessComputing, University of Washington}{Seattle, WA}{Dec. 2019}{\begin{cvitems}
\item Sponsored by The National Science Foundation (NSF).
\end{cvitems}}
    \cventry{Best Doctoral Proposal Fellowship}{The First International Conference on Quantitative Ethnography}{Madison, WI}{Oct. 2019}{\begin{cvitems}
\item Sponsored by Cengage.
\end{cvitems}}
    \cventry{Andrew V. Kozak Memorial Fellowship}{The PDK Educational Foundation}{University Park, PA}{2019}{\begin{cvitems}
\item Awarded \$1,500 for research contribution to public education.
\end{cvitems}}
    \cventry{AERA Pre-Conference Travel Award}{The Spencer Foundation}{Toronto, ON, Canada}{Apr. 2019}{}\vspace{-4.0mm}
    \cventry{Delta Gamma Golden Anchor Award}{The Pennsylvania State University}{University Park, PA}{2015, 2017}{}\vspace{-4.0mm}
    \cventry{ACM Richard Tapia Celebration of Diversity in Computing Conference Scholarship}{The National Science Foundation (NSF)}{Atlanta, GA}{Sep. 2017}{\begin{cvitems}
\item Included free conference registration, shared hotel accommodations and a \$500 travel stipend.
\end{cvitems}}
    \cventry{ACM Student Research Competition Travel Award}{Microsoft Research}{Atlanta, GA}{Sep. 2017}{\begin{cvitems}
\item \$500 travel stipend was awarded for ACM TAPIA 2017 Student Research Competition (SRC).
\end{cvitems}}
    \cventry{CSUN Conference Travel Award}{AccessComputing, University of Washington}{Seattle, WA}{Mar. 2017}{\begin{cvitems}
\item Sponsored by The National Science Foundation (NSF).
\end{cvitems}}
    \cventry{Summer Tuition Assistance Funding}{College of Education}{University Park, PA}{2017}{}\vspace{-4.0mm}
    \cventry{Graduate Student Travel Grant}{College of Education}{University Park, PA}{Aug. 2016 - Present}{}\vspace{-4.0mm}
    \cventry{Graduate Assistantship}{Teaching and Learning with Technology}{University Park, PA}{Aug. 2016 - Present}{}\vspace{-4.0mm}
    \cventry{Outstanding Academic Award}{Hyomyoung Scholarship}{Seoul, South Korea}{2014 - 2019}{}\vspace{-4.0mm}
    \cventry{All Nations Church Graduate Scholarship}{ANC Scholarship Foundation}{Lake View Terrace, CA}{2016}{}\vspace{-4.0mm}
\end{cventries}

\section{Service}\label{service}

\begin{cventries}
    \cventry{Search Committee for Director/Assistant Dean, Diversity, Equity, Inclusion, and Accessibility (DEIA)}{School of Information Sciences at the University of Illinois at Urbana-Champaign}{Champaign, IL}{April 2022 - Present}{}\vspace{-4.0mm}
    \cventry{Diversity Committee}{School of Information Sciences at the University of Illinois at Urbana-Champaign}{Champaign, IL}{Sep. 2021 - Apr. 2022}{}\vspace{-4.0mm}
    \cventry{Program Committee Member}{International Web for All Conference (W4A) 2022}{Virtual}{Dec. 2021 - Feb. 2022}{}\vspace{-4.0mm}
    \cventry{Accessibility Chair}{15th International Conference on Educational Data Mining}{Durham}{Oct. 2021 - Jul. 2022}{}\vspace{-4.0mm}
    \cventry{Journal Reviewer}{Special issue on ethnography and learning design}{TechTrends}{Sep. 2021}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The Network of Academic Programs in the Learning Sciences (NAPLeS)}{International Society of the Learning Sciences}{2020}{\begin{cvitems}
\item Reviewed abstracts on equity and disability.
\end{cvitems}}
    \cventry{College of Education Technology Committee}{The Pennsylvania State University}{University Park, PA}{Aug. 2019 - May. 2020}{\begin{cvitems}
\item Worked as a student committee member to support understanding of educational technology for College of Education.
\end{cvitems}}
    \cventry{Libraries' Accessibility Student Advisory Group}{The Pennsylvania State University}{University Park, PA}{Aug. 2019 - May. 2020}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 14th International Conference of the Learning Sciences (ICLS)}{Nashville, TN}{2019}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The ACM CHI Conference on Human Factors in Computing Systems (CHI 2020, 2021)}{Honolulu, HI, Yokohama, Japan}{2019, 2020}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 1st International Conference on Quantitative Ethnography (ICQE)}{Madison, WI}{2019}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 3rd Learning Sciences Graduate Student Conference (LSGSC)}{Nashville, TN}{2018}{}\vspace{-4.0mm}
    \cventry{Reviewer}{The 2nd Learning Sciences Graduate Student Conference (LSGSC)}{Bloomington, IN}{2017}{}\vspace{-4.0mm}
    \cventry{Funding Reviewer}{Center for Online Innovation in Learning (COIL), The Pennsylvania State University}{University Park, PA}{2016}{}\vspace{-4.0mm}
\end{cventries}

\section{Current Memberships}\label{current-memberships}

\begin{itemize}
\tightlist
\item
  International Society of the Learning Sciences (ISLS)
\item
  Association for Computing Machinery (ACM)
\item
  American Statistical Association (ASA)
\item
  International Society for Quantitative Ethnography (ISQE)
\item
  International Association of Accessibility Professionals (IAAP)
\item
  International Educational Data Mining Society (IEDMS)
\end{itemize}


\label{LastPage}~
\end{document}
